

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 7pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[margin=0.7in]{geometry}
\usepackage{fontawesome}
\usepackage{hyperref}

\usepackage{arev} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

\setlength{\textwidth}{5.8in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge\bf Abhinav Khare}\\% Your name at the top

%%\moveleft\hoffset\vbox{\hrule width 7in height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
%\moveleft.5\hoffset\centerline{1-9-7/a line no 13, Ravindra Nager} % Your address
%\moveleft.5\hoffset\centerline{Habsiguda,Hyderabad 500007}
%\moveleft.5\hoffset\centerline{+91 7660009419}
\moveleft.5\hoffset\centerline{ \href{https://github.com/CosmicCoder96}{\faGithub} \hspace{0.1cm}\textbullet \hspace{0.1cm}\href{https://abhinavkhare.me}{Website}\hspace{0.1cm}\textbullet \hspace{0.1cm}\href{https://www.linkedin.com/in/abhinav-khare-a4444213a/}{\faLinkedin}}
\moveleft.5\hoffset\centerline{ abhinav.khare31@gmail.com\hspace{0.1cm} \textbullet \hspace{0.1cm}+91-8319473031}
%----------------------------------------------------------------------------------------
\begin{resume}
\section{EDUCATION}  

\textbf{Indian Institute of Information Technology Allahabad} \hfill Expected July 2019
\begin{itemize}
\item Bachelors of Technology in Information Technology. 
\item CGPA (After 6 semesters): 8.49/10
\item \textbf{Relevant Coursework}: Software Engineering, Object Oriented Methodology, Database Management Systems, Operating Systems, Computer Organization & Architecture,Data Structures, Design, Analysis of Algorithms
\end{itemize} 

\section{EXPERIENCE}

\textbf{Google Summer of Code Student} \hfill May 2017 - July 2017 \\
FOSSASIA, Singapore
\begin{itemize}
\item Implemented flask framework programming fundamentals as part of the event organization server for FOSSASIA, with a focus on normalization.
\item Organized the processes around decoupling of back and front end with a focus on a complete redesign of the front end.
\end{itemize} 

\textbf{Remote Developer Part-time Intern} \hfill August 2017 - December 2017 \\
FOSSASIA
\begin{itemize}
\item Continued to work on the GSoC Open Event Project in an official capacity, as a remote developer
\end{itemize}

\textbf{Summer Research Intern} \hfill May 2018 - July 2018 \\
Universita Degli Studi di Messina/ Smartme.io Messina, Italy
\begin{itemize}
\item Worked on pioneering database tech - BigchainDB to replace CKAN based centralized data store of SmartME Project (smartme.io)
\item  Engineered a new decentralized storage architecture to accumulate readings from IoT Sensors spread across the city of Messina along with a novel data source verification mechanism.
\end{itemize} 

\textbf{Google Summer of Code Mentor}  \hfill May 2018 - August 2018 \\
Open Event Project, FOSSASIA
\begin{itemize}
    \item Supervised the Open Event project as the lead mentor during GSoC 2018.
    \item Played key role in transition from legacy system a new version
\end{itemize}

\textbf{Developer Intern} \hfill January 2019 - June 2019 \\
TL Labs, Nanyang Technological University, Singapore
\begin{itemize}
\item Will be working on engineering and designing a novel text editor, which automates the process of transcription verification in an NLP context.
\end{itemize}

\textbf{Summer School Student} \hfill June 2016 - July 2016\\
Harvard University, Boston, MA
\begin{itemize}
\item Introduction to programming course
\end{itemize} 
%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 


\section{PUBLICATIONS}
Khare, Abhinav, et al. "Trust-less Smart City: the #SmartME approach." {\sl Submitted to 5th IEEE World Forum in Limerick, Ireland, 2019.}  \hfill In review$

Khare, Abhinav, et al. "Learning the Goal Seeking Behaviour for Mobile Robots." {\sl 2018 3rd Asia-Pacific Conference on Intelligent Robot Systems (ACIRS). IEEE, 2018.} 

Patel, A. S., Ojha, M., Rani, M., Khare, A., Vyas, O. P., \& Vyas, R. (2018, June). Ontology-Based Multi-agent Smart Bike Sharing System (SBSS). {\sl In 2018 IEEE International Conference on Smart Computing (SMARTCOMP) (pp. 417-422). IEEE.} 

\section{SELECTED PROJECTS}
\textbf{Verifiable IoT Data Exchange} :- Semester project which iterates on the data verification wizard developed  during internship in Messina. It combines the wizard with the distributed database - bighcaindb and runs on a cluster of nodes. The platform allows the users to confidently sell and exchange data on account of it being verifiable

\textbf{Regression based Motion Planning}:- Implemented a neural network to simulate a robot to navigate obstacles and reach its goal using reinforcement learning. Compared results and accuracy by contrasting supervised learning approach with reinforcement learning approach.

\textbf{Flash Cards}:- Using UI/UX research, a minimal react JS based flash card app was developed, best designed to soothe the user and visually aid him/her while memorizing keywords. The app was published as an Open Source project and received critical acclaim from the community.


\section{ENTRE-PRENEURSHIP}
\textbf{Hack In The North}, Lead Organizer
\begin{itemize}
    \item Organised third edition of one of the most successful student held hackathon of India
    \item Secured sponsorship in excess of 5000\$ for the event including Python Software foundation, Github, Heroku, Consensys.
\end{itemize}


\section{COMMUNITY INVOLVEMENT}

\textbf{Technical Secretary}, Student Body IIIT Allahabad 
\begin{itemize}
    \item Elected as the technical secretary of the batch.
    \item Supervised the 9 technical wings of the tech society - GeekHaven
    \item Negotiated fundings, and oversaw the functioning of technical fest - Aparoksha
\end{itemize}
\textbf{Web Development Wing Member}, Geekhaven
\begin{itemize}
    \item Selected as a web developer in tech society of IIIT Allahabad.
    \item Conducted Workshops to teach web development to freshmen.
\end{itemize}
\textbf{Google Code In 2018}, Mentor for FOSSASIA
\begin{itemize}
    \item Guided young students to begin their journey into open source
    \item Created and reviewed the tasks assigned to students during program.
\end{itemize}

\section{EXTRA-CURRICULAR}
\begin{itemize}
    \item Head of Web Operations, Effervescence'17 - Cultural Fest, IIITA
    \item Head of Web Operations, Aparoksha'17 - Technical Fest, IIITA
    \item Head of Web Operations, Asmita'18 - Sports Fest, IIITA
    \item Organizer, IIITA Hacks - Promotional Hackathon
    \item Organizer, OpenCode - Promoted open source during winter break
    \item Member, Acoustic and Media Society, IIITA
\end{itemize}

\section{CONFERENCES \& TALKS}
\begin{itemize}
    \item Speaker, \textbf{Google Summer of Code Mentor Summit'18} \hfill{Sunnyvale, USA}
    \item Speaker,\textbf{FOSSASIA Summit 2018} \hfill{Singapore}
    \item Attendee, \textbf{IEEE International Conference on Smart Computing'18} \hfill{Sicily, Italy}
\end{itemize}


%----------------------------------------------------------------------------------------

\end{resume}
\end{document}